%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 2.0 (6/7/2019)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{article} % Default document font size

\input{structure.tex} % Include the file specifying the document structure and styling

% Set PDF meta-information
\hypersetup{
	pdftitle={Jude C. Nelson - Curriculum vitae},
	pdfauthor={Jude C. Nelson}
}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION
%----------------------------------------------------------------------------------------

{\LARGE\bfseries Jude C. Nelson} % Name
\bigskip\bigskip\medskip % Whitespace

Stacks Open Internet Foundation\\ % Address
1950 W. Corporate Way \#32788\\
Anaheim, CA 92801
\medskip % Whitespace

Email: \href{mailto:jude@stacks.org}{jude@stacks.org}\\ % Email address
\textsc{url}: \href{http://judecnelson.com}{http://judecnelson.com}\\ % Academic/personal website

\vspace{0.06\textheight} % Whitespace between contact information and specific CV information

%------------------------------------------------

% Burn: 19 January 1988---Burlington, VT, USA\\
Nationality: American

%------------------------------------------------

\section*{Current position}

\emph{Research Scientist}, Stacks Open Internet Foundation

%------------------------------------------------

\section*{Areas of specialisation}

Computer Science; Computer Networks; Peer-to-Peer Storage Systems

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section*{Appointments held}

\years{2009-2010}IBM Student Co-op, IBM Tucson\\
\years{2011-2012}Teaching Assistant, Princeton University\\
\years{2012-2016}Research Assistant, Princeton University\\
\years{2016-2020}Engineering Partner, Blockstack PBC\\
\years{2020-2021}Research Scientist, Stacks Open Internet Foundation\\

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section*{Education}

\years{2010}\textsc{BS} in Computer Science, University of Arizona\\
\years{2012}\textsc{MA} in Computer Science, Princeton University\\
\years{2018}\textsc{PhD} in Computer Science, Princeton University\\

%----------------------------------------------------------------------------------------
%	GRANTS, HONOURS AND AWARDS
%----------------------------------------------------------------------------------------

\section*{Grants, honors \& awards}

\years{2006}President's Award for Excellence Scholarship. \$24,000\\
\years{2017}CC*DNI DIBBS \#1541318, National Science Foundation. \$1,597,862\\

%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS
%----------------------------------------------------------------------------------------

\section*{Publications \& talks}

\subsection*{Conference proceedings}

\years{2014}Nelson, Jude; Peterson, Larry L. (2014), "Syndicate: Virtual Cloud Storage through Provider Composition," \emph{BigSystem '14}: 1-8. \url{https://doi.org/10.1145/2609441.2609639}\\
\years{2016a}Ali, Muneeb; Nelson, Jude; Shea, Ryan; Freedman, Michael J. (2016), "Blockstack: A Global Naming and Storage System Secured by Blockchains," \emph{USENIX Annual Technical Conference '16}: 181-194. \url{https://dl.acm.org/doi/10.5555/3026959.3026977}\\
\years{2016b}Nelson, Jude; Ali, Muneeb; Shea, Ryan; Freedman, Michael J. (2016),
"Extending Existing Blockchains with Virtualchain," \emph{Distributed
Cryptocurrencies and Consensus Ledgers '16}.\\

\subsection*{Magazine articles}

\years{2016}Ali, Muneeb; Nelson, Jude; Shea, Ryan; Freedman, Michael J. (2016),
"Bootstrapping Trust in Distributed Sytems with Blockchains," \emph{USENIX
;login:}: 41: 52-58.\\

\subsection*{Journal articles}

\years{2010}Nelson, Jude (2010), "An Improved Multiprotocol Application Data
Transfer Service," \emph{Technical Report}, University of Arizona.\\
\years{2018}Nelson, Jude (2018), "Wide-area Software-defined Storage," \emph{PhD dissertation}.\\

\subsection*{Talks}

\years{2011}Nelson, Jude; Peterson, Larry L. (2011), "Syndicate: A Scalable
Distributed Filesystem drivn by a Content Distribution Network." Internet2 Fall
2011 Member Meeting.  October 3-6, 2011. Raleigh, NC, USA.\\
\years{2018}Nelson, Jude (2018), "Subdomains: Scalable User Registration,"
Blockstack Berlin.  22 March 2018, Berlin, Germany. \url{https://www.youtube.com/watch?v=ffprmuFD_d8}\\
\years{2019}Nelson, Jude (2019), "The Stacks Blockchain," Decentralizing the
World Tour.  23 January 2019, Hong Kong, PRC. \url{https://www.youtube.com/watch?v=anj4BCs8GaI}\\
\years{2020}Nelson, Jude (2020), "Towards a User-Onwed Web," Naval Postgraduate
School.  22 May 2020, Monterey, CA, USA.

\subsection*{Patents}

\years{2020a}Nelson, Jude; Blankstein, Aaron; Salibra, Lawrence; et al. (24
March 2020).  "Platform and associated method for authenticating the identity of
a user in a decentralized system without need for a third-party identity
service."  US Patent No. \#10,601,829.\\
\years{2020b}Blankstein, Aaron; Nelson, Jude; Salibra, Lawrence; et al. (28
April 2020).  "Migrating data for decentralized applications between disparate
backend storage providers."  US Patent No. \#10,637,666.\\
\years{2020c}Liao, Yukan; Little, Matthew; Nelson, Jude; et al. (26 May 2020).
"Systems and methods for encrypting data in backend storage caches shared by
multiple decentralized applications."  US Patent No. \#10,664,451.\\
\years{2020d}Nelson, Jude. (30 June 2020).  "Systems and methods for forming application-specific
blockchains."  US Patent No. \#10,698,728.\\
\years{2020e}Blankstein, Aaron; Nelson, Jude. (30 June 2020).  "System and method for smart
contract publishing."  US Patent No. \#10,699,269.\\
\years{2020f}Blankstein, Aaron; Nelson, Jude; Salibra, Lawrence; et al. (29
December 2020).  "Backup of encrypted information stored off-chain in a
blockchain-based decentralized storage system."  US Patent No. \#10,880,076.\\

% Any final footer text such as a URL to the latest version of this CV, last updated date, compiled in XeTeX, etc
\begin{center}
	\scriptsize
	Last updated: \today
\end{center}

%----------------------------------------------------------------------------------------

\end{document}
